\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-17 manuscript.Rmd
looping

```{r depMan, eval=FALSE, include=FALSE}
library(packrat)
#This chunk is disabled. Only run this to install the dependencies automatically.
packrat::init()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")
remotes::install_github("jthomasmock/gtExtras")
install.packages("questionr")
devtools::install_github("lbusett/insert_table")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(kutils)
r_refs("references.bib")
```

@@

| Visual Light Sensitivity Questionnaire-8        | a       | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |

@@

```{r EFAdata, include=FALSE}
### EFA data
EFA.data <- sem.data[1:428, ]
```

@@

n1 <- shapiro.test(EFA.data$item1)
n2 <- shapiro.test(EFA.data$item2)
n3 <- shapiro.test(EFA.data$item3)
n4 <- shapiro.test(EFA.data$item4)
n5 <- shapiro.test(EFA.data$item5)
n6 <- shapiro.test(EFA.data$item6)
n7 <- shapiro.test(EFA.data$item7)
n8 <- shapiro.test(EFA.data$item8)
n9 <- shapiro.test(EFA.data$item9)
n10 <- shapiro.test(EFA.data$item10)
n11 <- shapiro.test(EFA.data$item11)
n12 <- shapiro.test(EFA.data$item12)
n13 <- shapiro.test(EFA.data$item13)
n14 <- shapiro.test(EFA.data$item14)
n15 <- shapiro.test(EFA.data$item15)
n16 <- shapiro.test(EFA.data$item16)
n17 <- shapiro.test(EFA.data$item17)
n18 <- shapiro.test(EFA.data$item18)
n19 <- shapiro.test(EFA.data$item19)
n20 <- shapiro.test(EFA.data$item20)
n21 <- shapiro.test(EFA.data$item21)
n22 <- shapiro.test(EFA.data$item22)
n23 <- shapiro.test(EFA.data$item23)
n24 <- shapiro.test(EFA.data$item24)
n25 <- shapiro.test(EFA.data$item25)
n26 <- shapiro.test(EFA.data$item26)
n27 <- shapiro.test(EFA.data$item27)
n28 <- shapiro.test(EFA.data$item28)
n29 <- shapiro.test(EFA.data$item29)
n30 <- shapiro.test(EFA.data$item30)
n31 <- shapiro.test(EFA.data$item31)
n32 <- shapiro.test(EFA.data$item32)
n33 <- shapiro.test(EFA.data$item33)
n34 <- shapiro.test(EFA.data$item34)
n35 <- shapiro.test(EFA.data$item35)
n36 <- shapiro.test(EFA.data$item36)
n37 <- shapiro.test(EFA.data$item37)
n38 <- shapiro.test(EFA.data$item38)
n39 <- shapiro.test(EFA.data$item39)
n40 <- shapiro.test(EFA.data$item40)
n41 <- shapiro.test(EFA.data$item41)
n42 <- shapiro.test(EFA.data$item42)
n43 <- shapiro.test(EFA.data$item43)
n44 <- shapiro.test(EFA.data$item44)
n45 <- shapiro.test(EFA.data$item45)
n46 <- shapiro.test(EFA.data$item46)
n47 <- shapiro.test(EFA.data$item47)
n48 <- shapiro.test(EFA.data$item48)

normality.tab = matrix(, nrow = 48, ncol = 2)
as.table(normality.tab)
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(normality.tab) <- my.item.names
colnames(normality.tab) <- c("statistic", "p")

normality.tab[,1] <- c(apa((n1$statistic),2,T),
                       apa((n1$statistic),2,T),
                       apa((n3$statistic),2,T),
                       apa((n4$statistic),2,T),
                       apa((n5$statistic),2,T),
                       apa((n6$statistic),2,T),
                       apa((n7$statistic),2,T),
                       apa((n8$statistic),2,T),
                       apa((n9$statistic),2,T),
                       apa((n10$statistic),2,T),
                       apa((n11$statistic),2,T),
                       apa((n12$statistic),2,T),
                       apa((n13$statistic),2,T),
                       apa((n14$statistic),2,T),
                       apa((n14$statistic),2,T),
                       apa((n16$statistic),2,T),
                       apa((n17$statistic),2,T),
                       apa((n18$statistic),2,T),
                       apa((n19$statistic),2,T),
                       apa((n20$statistic),2,T),
                       apa((n21$statistic),2,T),
                       apa((n22$statistic),2,T),
                       apa((n23$statistic),2,T),
                       apa((n24$statistic),2,T),
                       apa((n25$statistic),2,T),
                       apa((n26$statistic),2,T),
                       apa((n27$statistic),2,T),
                       apa((n28$statistic),2,T),
                       apa((n29$statistic),2,T),
                       apa((n30$statistic),2,T),
                       apa((n31$statistic),2,T),
                       apa((n32$statistic),2,T),
                       apa((n33$statistic),2,T),
                       apa((n34$statistic),2,T),
                       apa((n35$statistic),2,T),
                       apa((n36$statistic),2,T),
                       apa((n37$statistic),2,T),
                       apa((n38$statistic),2,T),
                       apa((n39$statistic),2,T),
                       apa((n40$statistic),2,T),
                       apa((n41$statistic),2,T),
                       apa((n42$statistic),2,T),
                       apa((n43$statistic),2,T),
                       apa((n44$statistic),2,T),
                       apa((n45$statistic),2,T),
                       apa((n46$statistic),2,T),
                       apa((n47$statistic),2,T),
                       apa((n48$statistic),2,T))

normality.tab[,2] <- c(apa((n1$p.value),2,T),
                       apa((n1$p.value),2,T),
                       apa((n3$p.value),2,T),
                       apa((n4$p.value),2,T),
                       apa((n5$p.value),2,T),
                       apa((n6$p.value),2,T),
                       apa((n7$p.value),2,T),
                       apa((n8$p.value),2,T),
                       apa((n9$p.value),2,T),
                       apa((n10$p.value),2,T),
                       apa((n11$p.value),2,T),
                       apa((n12$p.value),2,T),
                       apa((n13$p.value),2,T),
                       apa((n14$p.value),2,T),
                       apa((n14$p.value),2,T),
                       apa((n16$p.value),2,T),
                       apa((n17$p.value),2,T),
                       apa((n18$p.value),2,T),
                       apa((n19$p.value),2,T),
                       apa((n20$p.value),2,T),
                       apa((n21$p.value),2,T),
                       apa((n22$p.value),2,T),
                       apa((n23$p.value),2,T),
                       apa((n24$p.value),2,T),
                       apa((n25$p.value),2,T),
                       apa((n26$p.value),2,T),
                       apa((n27$p.value),2,T),
                       apa((n28$p.value),2,T),
                       apa((n29$p.value),2,T),
                       apa((n30$p.value),2,T),
                       apa((n31$p.value),2,T),
                       apa((n32$p.value),2,T),
                       apa((n33$p.value),2,T),
                       apa((n34$p.value),2,T),
                       apa((n35$p.value),2,T),
                       apa((n36$p.value),2,T),
                       apa((n37$p.value),2,T),
                       apa((n38$p.value),2,T),
                       apa((n39$p.value),2,T),
                       apa((n40$p.value),2,T),
                       apa((n41$p.value),2,T),
                       apa((n42$p.value),2,T),
                       apa((n43$p.value),2,T),
                       apa((n44$p.value),2,T),
                       apa((n45$p.value),2,T),
                       apa((n46$p.value),2,T),
                       apa((n47$p.value),2,T),
                       apa((n48$p.value),2,T))

normalityprefix <- normality.tab[,1]
normalitysufix <- "*"
normality.names <- paste(normalityprefix,normalitysufix, sep = "" )

@@

Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), normality.names,  apa(Item.total$r.cor,2,F))

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")

rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)
```

@@

```{r facIdFig, out.height="120%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

F1_info <- plot(F1_fit, type = "infoSE", main = "F1")

F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")

F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")

F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")

F5_info <- plot(F5_fit, type = "infoSE", main = "F5")

Test_Info <- plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

@@

```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)

>>>>

```{r depMan, eval=FALSE, include=FALSE}
library(packrat)
#This chunk is disabled. Only run this to install the dependencies automatically.
packrat::init()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)

@@

install.packages("devtools")
install.packages("semTools")
install.packages("MOTE")
install.packages("psych")
install.packages("dlookr")
install.packages("tidyverse")
install.packages("qgraph")
install.packages("kableExtra")
install.packages("paran")
install.packages("EFA.MRFA")
install.packages("rsvg")
install.packages("ggcorrplot")
install.packages("semTable")
install.packages("magick")
install.packages("mirt")
install.packages("cowplot")
install.packages("VIM")
devtools::install_github('rich-iannone/DiagrammeR')
devtools::install_github("crsh/papaja", force = T)
install.packages("DiagrammeRsvg")
devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
devtools::install_github("crsh/citr")
remotes::install_github("jthomasmock/gtExtras")
install.packages("gt")
remotes::install_github("jthomasmock/gtExtras")
install.packages("questionr")
devtools::install_github("lbusett/insert_table")
```

@@

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#revercoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
r_refs("references.bib")
```

@@

| Visual Light Sensitivity Questionnaire-8        |         | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |

@@

```{r EFAdata, include=FALSE}
### EFA data
EFA.data <- sem.data[1:428, ]
#library(VIM)
missing <- aggr(EFA.data, plot =T)

@@

#creating normality function
shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
  l <- lapply(df, shapiro.test)
  s <- do.call("c", lapply(l, "[[", 1))
  p <- do.call("c", lapply(l, "[[", 2))
  if (bonf == TRUE) {
    sig <- ifelse(p > alpha / length(l), "H0", "*")
  } else {
    sig <- ifelse(p > alpha, "H0", "*")
  }
  return(list(statistic= s,
              p.value= p,
              significance= sig,
              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
                             "Shapiro-Wilks test without Bonferroni Correction")))
}

Shapiro.efa <- shapiro_test_df(EFA.data)

efa.normality.tab = matrix(nrow = 48, ncol = 2)
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(efa.normality.tab) <- my.item.names
colnames(efa.normality.tab) <- c("statistic", "p")

efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)

efa.normalityprefix <- efa.normality.tab[,1]
efa.normalitysufix <- Shapiro.efa$significance
efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )

@@

Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))

colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
rownameprefix <- "Item"
rownamesufix <- seq(1:48)
my.names <- paste(rownameprefix,rownamesufix, sep = "" )
rownames(Des.combined) = (my.names)
```

@@

```{r facIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

F1_item.info <- plot(F1_fit, type = "infotrace", main = "F1")

F2_item.info.redu <- plot(F2_fit.redu, type = "infotrace", main = "F2")

F3_item.info.redu <- plot(F3_fit.redu, type = "infotrace", main = "F3")

F4_item.info.redu <- plot(F4_fit.redu, type = "infotrace", main = "F4")

F5_item.info <- plot(F5_fit, type = "infotrace", main = "F5")

@@

```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
plot_grid(F1_item.info, F2_item.info.redu,F3_item.info.redu,F4_item.info.redu,F5_item.info, 
          labels = "AUTO", label_size = 10)
